Backpropagating Gravitational wave events

### 2022-05-20 src/ms.tex
Minor typo fixes in results section.

We show a portion of the joint posterior of the progenitor parameters 
and hyperparameters of GW150914 in figure \ref{fig:GW150914_posterior}. 
Each panel is colored based on the comparison between progenitor parameters (blue), hyperparameters (orange), or 
a mix of the two (green). 
We find that the choice for $\sigma$ does not affect the formation of GW150914-like BBHs. This is not unexpected 
since we use the \citet{Fryer2012} delayed model which reduces the natal kick strength at BH formation based on the amount
of fallback onto the proto-CO. In the case of GW150914-like BBHs, the BH progenitors are massive enough that the 
fallback reduces the natal kick to zero. Because of this we do not include $\sigma$ in Figure~\ref{fig:GW150914_posterior}.
Similarly, we do not include the ZAMS orbital period and eccentricity are correlated with one another, but not strongly with the other progenitor
parameters or hyperparameters. We find strong correlations in the ZAMS masses, as well as 
strong correlations between $M_{2,\rm{ZAMS}}$ and $f_{\rm{acc}}$ and $f_{\rm{acc}}$ and $\alpha$. We show scatter points of each of these 
combinations in the upper-right inset of the figure.

>>>>

We show a portion of the joint posterior of the progenitor parameters and
hyperparameters of GW150914 in figure \ref{fig:GW150914_posterior}. Each panel
is colored based on the comparison between progenitor parameters (blue),
hyperparameters (orange), or a mix of the two (green). We find that the choice
for $\sigma$ does not affect the formation of GW150914-like BBHs. This is not
unexpected since we use the \citet{Fryer2012} delayed model which reduces the
natal kick strength at BH formation based on the amount of fallback onto the
proto-CO. In the case of GW150914-like BBHs, the BH progenitors are massive
enough that the fallback reduces the natal kick to zero. Because of this we do
not include $\sigma$ in Figure~\ref{fig:GW150914_posterior}. Similarly, we do
not include the ZAMS orbital period and eccentricity, which are correlated with
one another, but not strongly with the other progenitor parameters or
hyperparameters. We find strong correlations between the ZAMS masses, as well as
strong correlations between $M_{2,\rm{ZAMS}}$ and $f_{\rm{acc}}$, and
$f_{\rm{acc}}$ and $\alpha$. We show scatter plots of each of these combinations
in the upper-right inset of the figure.
